\documentclass[line,margin]{res}
\addtolength{\textheight}{1in}
\addtolength{\topmargin}{-40px}
\addtolength{\oddsidemargin}{-20px}
\addtolength{\textwidth}{30px}
\usepackage{changepage}
%\usepackage[margin=0.5in]{geometry}
%\usepackage{helvetica}	% uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}	% uses new century schoolbook postscript font 
%\usepackage{

\begin{document}

\name{ALAN Y. HUANG}
%\address{4218 NE Meadow Ln. Hillsboro OR 97124}				% \address used twice to have two lines of address
\address{Phone: +1.650.772.1711 $|$ Email: alan.huang.250r@gmail.com}

\begin{resume}

% \vspace{-10px}
% \section{SUMMARY}
% \vspace{25px}
% \begin{adjustwidth}{-115pt}{0pt}
% \begin{itemize}
% 	\item Experinced in deploying and managing on-prem and cloud infrastructures. Leveraged IaC technologies as well as automation development/programming, node triage, and POC development and deployment.
% \end{itemize}
% \end{adjustwidth}

\section{EXPERIENCE}
\vspace{25px}
\begin{adjustwidth}{-115pt}{0pt}
	{\sl Site Reliability Engineer}
		\hfill October 2021 - Present\\
		Slickdeals, Platforms Team - Las Vegas, NV (Remote)
		\begin{itemize}
			%\itemsep -2pt
			\item Managed and deployed both on-prem and cloud infrastructure utilizing IaC platforms such as Chef and Terraform.
				\subitem - Created and managed Chef cookbooks for deploying and unit testing services to on-prem nodes as well as for AMI creation for EC2 instances.
				\subitem - Created and managed Terraform code to deploy infrastructure such as EKS clusters and various AWS services such as S3, IAM, Route53, and Security Groups
			\item Managing technology lifecycle from SPIKE, to POC, to implementation and deployment.
				\subitem - Researched, deployed, and owned EKS cluster for production and development workloads.
				\subitem - Enabling EKS technologies to optimize workloads in the cloud (auto scalers, PVCs, certificate management).
				\subitem - Deployed Nexus Repository Manager to EKS in support of cloud migration initiative.
			\item Member of Cloud Migration Team focusing on architecting, deploying, and managing cloud solutions to replace on-prem technologies.
				\subitem - Owning database migration project to migrate MySQL5.6 to MySQL8 in preparation for RDS deployment.
				\subitem - Manage relationship with 3rd party database vendor Percona and acted as primary point of contact.

		\end{itemize}
	\hfill\\
	{\sl CAD Engineer}
		\hfill July 2018 - October 2021\\
		Synopsys, Solutions Group - Hillsboro OR
		\begin{itemize}
			%\itemsep -2pt
			\item Streamlined IP release process by creating automated repository sync and management tool.
				\subitem - Leveraged technologies such as Javascript/jQuery, Python, and Git. 
			\item Designed and manage VM infrastructure (assigning resources, load balancing, VM deployments) used for hosting automations, service hosts, and custom VMs.
			\item Develop and maintain automation infrastructure and compute hosts.
				\subitem - Debugging of Linux hosts, investigating new technologies, and deploying services and automations.
			\item Liaison and “fixer” for engineering and IT communications and joint projects.
		\end{itemize}
	\hfill\\
	{\sl Linux Systems Engineer}
		\hfill June 2015 - July 2018\\
		Synopsys, Information Technology and Engineering Support - Hillsboro OR
		\begin{itemize}
			%\itemsep -2pt
			\item Worked closely with several international teams during acquisitions for integration of their compute environment to ensure a smooth bring up.
			\item Managed local datacenter including network/storage appliances. Responsibilities included the entire lifecycle of servers: purchase, physical installation, provision/management, removal and retirement.
			\item Participation in 24/7 on-call as well as disaster recovery operations.
			\item Work with engineering teams for development of joint automations, services, and tools.
			\item Project lead for site networking upgrade including datacenter backbones, floor networks, and wireless networks.
%				\subitem - Coordinated work with contractors and facilities for fiber and facilities hardware installation.
%				\subitem - Cabled and installed all datacenter backbone switches, floor IDFs, and networking endpoints.
			\item Daily responsibilities include monitoring datacenter health, Linux host triage/debug, deployment/scaling of IT services, automations, and tools.
		\end{itemize}

	%\hfill\\
	%\vspace{-10pt}	
%	{\sl Bioacoustics Signal Processing Research Assistant}
%		\hfill June 2013 - June 2015\\
%		Oregon State University, College of Engineering - Corvallis OR
%		\begin{itemize}
%			%\itemsep -2pt
%			\item Created MATLAB tool set for filtering audio data to generate, whiten, classify, and segment spectrograms.
%			\item Developed a MATLAB GUI tool for inspecting spectrograms in order to more efficiently develop and test classifiers for spectrogram whitening algorithms.
%			\item Developed tool set is now being used for both avian and underwater audio analysis.
%		\end{itemize}

%	{\sl IT Support Associate}
%		\hfill April 2012 - June 2015\\
%		Oregon State University, College of Engineering - Corvallis OR
%		\begin{itemize}
%			\itemsep -2pt
%			\item Provide IT support for students and staff in the College of Engineering.
%			\item Manage and deploy compute assets such as computers, monitors, and printers to staff in the College of Engineering.
%			\item Monitor and maintain computer lab assets including computers, printers, and presentation equipment such as projectors.
%		\end{itemize}
\end{adjustwidth}

\section{TECHNICAL SKILLS}
\vspace{25px}
\begin{adjustwidth}{-115pt}{0pt}
	\begin{itemize}
		%\itemsep - 2pt
		\item Programming: Python, BASH, C/Cpp, Perl, Ruby, TCL, Assembly, AVR, MATLAB, \LaTeX, SQL
		\item DevOps/SRE: AWS, Kubernetes/EKS, Docker/Compose, Terraform, SGE, LSF, Helm, Rancher, Elasticsearch, Nagios, Chef, Jenkins, Ansible, Jira, Git, Perforce, Linux
		% \item DevOps Principles: Load balancing, microservices, robust architecture design, networking, NFS/storage, CD/CI
		% \item Operating Systems: CentOS, RHEL, Ubuntu, Windows, MacOS
		\item Front-End: JavaScript, jQuery, HTML, CSS, Flask, PHP, Sharepoint
	\end{itemize}
\end{adjustwidth}

%\section{TECHNICAL SKILLS}
%	\begin{itemize}
%		\itemsep - 2pt
%		\item Computer Engineering and IT Skills:
%			\subitem - Programming: C, C++, Python, MAKE, BASH, Perl, \LaTeX, SQL, TCL
%			\subitem - Web Development: Javascript, JQuery, Sharepoint, C\#, .NET, PHP
%			\subitem - Dev-Ops: Linux, Jenkins, Chef, Virtualization, Perforce, Docker
%			\\
%		\item Electrical Engineering Skills:
%			\subitem - Engineering: Prototyping, Embedded, FPGA, Layout, Power Electronics
%			\subitem - Simulation Tools: MATLAB, HSPICE, Verilog/System Verilog, Xilinx ISE
%			\subitem - EDA Tools: Virtuoso, Eagle, LTSpice, Design Compiler, ModelSim
%			\subitem - Lab: Oscilloscopes, SMD Reflow, Signal Generators, Machining Tools
%	\end{itemize}

%\section{PROJECTS}
%{\sl Senior Design: Smart Disk}
%	\hfill Oregon State University 2014-2015\\
%	Small Form Factor Power Regulator that Provides Wireless Control via RF
%	\begin{itemize}
%		\itemsep -2pt
%		\item Lead developer and liaison with project stakeholder
%		\item Worked with engineering business group for parts and equipment
%		\item Developed small form factor buck converter for 110VAC with wireless RF control
%		\item 2015 OSU Senior Design Fair runner up for best project
%	\end{itemize}

\section{EDUCATION}
\vspace{25px}
\begin{adjustwidth}{-115pt}{0pt}
	{\sl Oregon State University, Corvallis, OR}
		\hfill Class of 2015 \\
			Bachelor of Science in Electrical and Computer Engineering - Analog Design
\end{adjustwidth}

\end{resume}
\end{document}
